Supplementary tables and figures for "Spatio-temporal estimates of HIV risk group proportions for adolescent

### 2022-06-17 src/docs_paper/tables-figures.Rmd
Variance proportions, prevalence plots into appendix B. Changes to captions #128

# Additional figures

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics{depends/model-direct-benefits.pdf}}
\caption{Illustration our model results for AGYW 20-24 in Tanzania in 2010 in the cohabiting risk group. Compared to the direct survey results, our spatio-temporally smoothed estimates more plausibly represent district level heterogeneity, as well as imputing any districts with missing data.}
\label{fig:model-direct-benefits}
\end{figure}

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{lX}
\toprule
Prioritisation strata & Criterion \\
\midrule
Low & 0.3-1\% incidence AND low-risk behaviour OR $<$0.3\% incidence AND high-risk behaviour \\
Moderate & 1-3\% incidence AND low-risk behaviour OR 0.3-1\% incidence AND high-risk behaviour \\
High & 1-3\% incidence AND high-risk behaviour \\
Very high & $>$3\% incidence \\
\bottomrule
\end{tabularx}
\caption{Prioritisation strata.}
\label{tab:unaids-strategy-prioritisation}
\end{table}

@@

# Survey data

@@

\caption{All surveys that we used in our analysis and their sample sizes.}

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{lX}
\toprule
Survey & Exclusion reason \\ 
 \midrule
MOZ2003DHS & No GPS coordinates available to place survey clusters within districts. \\
TZA2015DHS & Insufficient sexual behaviour questions. \\
UGA2004AIS & Unable to download region boundaries. \\
ZMB2002DHS & No GPS coordinates available to place survey clusters within districts. \\
\bottomrule
\end{tabularx}
\label{tab:surveys-excluded}
\caption{All surveys excluded from our analysis.}
\end{table}

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{lXX}
\toprule
Country & Number of areas & Analysis level \\ 
\midrule
Botswana & 27 & 3 \\ 
Cameroon & 58 & 2 \\ 
Kenya & 47 & 2 \\ 
Lesotho & 10 & 1 \\ 
Mozambique & 161 & 3 \\ 
Malawi & 33 & 5 \\ 
Namibia & 38 & 2 \\ 
Eswatini & 4 & 1 \\ 
Tanzania & 195 & 4 \\ 
Uganda & 136 & 3 \\ 
South Africa & 52 & 2 \\ 
Zambia & 116 & 2 \\ 
Zimbabwe & 63 & 2 \\ 
\bottomrule
\end{tabularx}
\label{tab:area-levels}
\caption{The numer of areas and analysis levels used in our analysis.}
\end{table}

@@

# Survey questions and risk group allocation

@@

@@

# National direct and modelled estimates comparison

@@

# Cloropleths

@@

@@

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=1]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Botswana.}
    \label{fig:incidence-district-sexbehav-1}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=2]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Cameroon.}
    \label{fig:incidence-district-sexbehav-2}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=3]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Kenya.}
    \label{fig:incidence-district-sexbehav-3}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=4]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Lesotho.}
    \label{fig:incidence-district-sexbehav-4}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=5]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Mozambique.}
    \label{fig:incidence-district-sexbehav-5}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=6]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Malawi.}
    \label{fig:incidence-district-sexbehav-6}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=7]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Namibia.}
    \label{fig:incidence-district-sexbehav-7}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=8]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Eswatini.}
    \label{fig:incidence-district-sexbehav-8}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=9]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Tanzania.}
    \label{fig:incidence-district-sexbehav-9}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=10]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Uganda.}
    \label{fig:incidence-district-sexbehav-10}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=11]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in South Africa.}
    \label{fig:incidence-district-sexbehav-11}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=12]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Zambia.}
    \label{fig:incidence-district-sexbehav-12}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=13]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Zimbabwe.}
    \label{fig:incidence-district-sexbehav-13}
\end{figure}

@@

# Infections reached

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=1]{depends/infections-reached-country.pdf}}
\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Botswana.}
\label{fig:infections-reached-country-1}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=2]{depends/infections-reached-country.pdf}}
\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Cameroon.}
\label{fig:infections-reached-country-2}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=3]{depends/infections-reached-country.pdf}}
\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Kenya.}
\label{fig:infections-reached-country-3}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=4]{depends/infections-reached-country.pdf}}
\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Lesotho.}
\label{fig:infections-reached-country-4}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=5]{depends/infections-reached-country.pdf}}
\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Mozambique.}
\label{fig:infections-reached-country-5}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=6]{depends/infections-reached-country.pdf}}
\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Malawi.}
\label{fig:infections-reached-country-6}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=7]{depends/infections-reached-country.pdf}}
\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Namibia.}
\label{fig:infections-reached-country-7}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=8]{depends/infections-reached-country.pdf}}
\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Eswatini.}
\label{fig:infections-reached-country-8}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=9]{depends/infections-reached-country.pdf}}
\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Tanzania.}
\label{fig:infections-reached-country-9}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=10]{depends/infections-reached-country.pdf}}
\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Uganda.}
\label{fig:infections-reached-country-10}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=11]{depends/infections-reached-country.pdf}}
\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in South Africa.}
\label{fig:infections-reached-country-11}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=12]{depends/infections-reached-country.pdf}}
\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zambia.}
\label{fig:infections-reached-country-12}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=13]{depends/infections-reached-country.pdf}}
\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zimbabwe.}
\label{fig:infections-reached-country-13}
\end{figure}

>>>>

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{lX}
\toprule
Prioritisation strata & Criterion \\
\midrule
Low & 0.3-1.0\% incidence and low-risk behaviour, or $<$0.3\% incidence and high-risk behaviour \\
Moderate & 1.0-3.0\% incidence and low-risk behaviour, or 0.3-1.0\% incidence and high-risk behaviour \\
High & 1.0-3.0\% incidence and high-risk behaviour \\
Very high & $>$3.0\% incidence \\
\bottomrule
\end{tabularx}
\caption{Prioritisation strata.}
\label{tab:unaids-strategy-prioritisation}
\end{table}

@@

# Household survey data

## Included surveys

@@

\caption{All of the surveys that we used in our analysis and their sample sizes, disaggregated by respondent age.}

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{lX}
\toprule
Survey & Exclusion reason \\ 
 \midrule
MOZ2003DHS & No GPS coordinates available to place survey clusters within districts. \\
TZA2015DHS & Insufficient sexual behaviour questions. \\
UGA2004AIS & Unable to download region boundaries. \\
ZMB2002DHS & No GPS coordinates available to place survey clusters within districts. \\
\bottomrule
\end{tabularx}
\label{tab:surveys-excluded}
\caption{All of that surveys that were excluded from our analysis.}
\end{table}

@@

## Spatial analysis levels

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{lXX}
\toprule
Country & Number of areas & Analysis level \\ 
\midrule
Botswana & 27 & 3 \\ 
Cameroon & 58 & 2 \\ 
Kenya & 47 & 2 \\ 
Lesotho & 10 & 1 \\ 
Mozambique & 161 & 3 \\ 
Malawi & 33 & 5 \\ 
Namibia & 38 & 2 \\ 
Eswatini & 4 & 1 \\ 
Tanzania & 195 & 4 \\ 
Uganda & 136 & 3 \\ 
South Africa & 52 & 2 \\ 
Zambia & 116 & 2 \\ 
Zimbabwe & 63 & 2 \\ 
\bottomrule
\end{tabularx}
\label{tab:area-levels}
\caption{The numer of areas and analysis levels for each country that were used in our analysis.}
\end{table}

## Survey questions

@@

## Risk group allocation

@@

# Miscellaneous figures

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics{depends/model-direct-benefits.pdf}}
\caption{Illustration our model results for AGYW 20-24 in Tanzania in 2010 in the cohabiting risk group. Compared to the direct survey results, our spatio-temporally smoothed estimates more plausibly represent district-level heterogeneity, as well as imputing any districts with missing data.}
\label{fig:model-direct-benefits}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics{depends/aaa-variance-proportions.pdf}}
    \caption{Proportion of variance explained by each random effect (Sobol' indices) when the multinomial regression model is fit to each country individually. In this setting, country-category random effects are not included in the model and year-category random effects are replaced by survey-category random effects (for countries with surveys in multiple years). Countries are ordered by the proportion of their variance which is explained by the area-category random effects.}
\label{fig:aaa-variance-proportions}
\end{figure}

# Country-specific figures

## Comparison of direct and modelled risk group estimates

@@

@@

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=1]{depends/prev-district-sexbehav-logit.pdf}}
    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Botswana.}
    \label{fig:prevalence-district-sexbehav-1}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=2]{depends/prev-district-sexbehav-logit.pdf}}
    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Cameroon.}
    \label{fig:prevalence-district-sexbehav-2}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=3]{depends/prev-district-sexbehav-logit.pdf}}
    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Kenya.}
    \label{fig:prevalence-district-sexbehav-3}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=4]{depends/prev-district-sexbehav-logit.pdf}}
    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Lesotho.}
    \label{fig:prevalence-district-sexbehav-4}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=5]{depends/prev-district-sexbehav-logit.pdf}}
    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Mozambique.}
    \label{fig:prevalence-district-sexbehav-5}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=6]{depends/prev-district-sexbehav-logit.pdf}}
    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Malawi.}
    \label{fig:prevalence-district-sexbehav-6}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=7]{depends/prev-district-sexbehav-logit.pdf}}
    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Namibia.}
    \label{fig:prevalence-district-sexbehav-7}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=8]{depends/prev-district-sexbehav-logit.pdf}}
    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Eswatini.}
    \label{fig:prevalence-district-sexbehav-8}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=9]{depends/prev-district-sexbehav-logit.pdf}}
    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Tanzania.}
    \label{fig:prevalence-district-sexbehav-9}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=10]{depends/prev-district-sexbehav-logit.pdf}}
    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Uganda.}
    \label{fig:prevalence-district-sexbehav-10}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=11]{depends/prev-district-sexbehav-logit.pdf}}
    \caption{District-level HIV prevalence for each of the risk groups in 2018 in South Africa.}
    \label{fig:prevalence-district-sexbehav-11}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=12]{depends/prev-district-sexbehav-logit.pdf}}
    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Zambia.}
    \label{fig:prevalence-district-sexbehav-12}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=13]{depends/prev-district-sexbehav-logit.pdf}}
    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Zimbabwe.}
    \label{fig:prevalence-district-sexbehav-13}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=1]{depends/incidence-district-sexbehav.pdf}}
    \caption{District-level HIV incidence for each of the risk groups in 2018 in Botswana.}
    \label{fig:incidence-district-sexbehav-1}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=2]{depends/incidence-district-sexbehav.pdf}}
    \caption{District-level HIV incidence for each of the risk groups in 2018 in Cameroon.}
    \label{fig:incidence-district-sexbehav-2}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=3]{depends/incidence-district-sexbehav.pdf}}
    \caption{District-level HIV incidence for each of the risk groups in 2018 in Kenya.}
    \label{fig:incidence-district-sexbehav-3}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=4]{depends/incidence-district-sexbehav.pdf}}
    \caption{District-level HIV incidence for each of the risk groups in 2018 in Lesotho.}
    \label{fig:incidence-district-sexbehav-4}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=5]{depends/incidence-district-sexbehav.pdf}}
    \caption{District-level HIV incidence for each of the risk groups in 2018 in Mozambique.}
    \label{fig:incidence-district-sexbehav-5}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=6]{depends/incidence-district-sexbehav.pdf}}
    \caption{District-level HIV incidence for each of the risk groups in 2018 in Malawi.}
    \label{fig:incidence-district-sexbehav-6}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=7]{depends/incidence-district-sexbehav.pdf}}
    \caption{District-level HIV incidence for each of the risk groups in 2018 in Namibia.}
    \label{fig:incidence-district-sexbehav-7}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=8]{depends/incidence-district-sexbehav.pdf}}
    \caption{District-level HIV incidence for each of the risk groups in 2018 in Eswatini.}
    \label{fig:incidence-district-sexbehav-8}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=9]{depends/incidence-district-sexbehav.pdf}}
    \caption{District-level HIV incidence for each of the risk groups in 2018 in Tanzania.}
    \label{fig:incidence-district-sexbehav-9}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=10]{depends/incidence-district-sexbehav.pdf}}
    \caption{District-level HIV incidence for each of the risk groups in 2018 in Uganda.}
    \label{fig:incidence-district-sexbehav-10}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=11]{depends/incidence-district-sexbehav.pdf}}
    \caption{District-level HIV incidence for each of the risk groups in 2018 in South Africa.}
    \label{fig:incidence-district-sexbehav-11}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=12]{depends/incidence-district-sexbehav.pdf}}
    \caption{District-level HIV incidence for each of the risk groups in 2018 in Zambia.}
    \label{fig:incidence-district-sexbehav-12}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=13]{depends/incidence-district-sexbehav.pdf}}
    \caption{District-level HIV incidence for each of the risk groups in 2018 in Zimbabwe.}
    \label{fig:incidence-district-sexbehav-13}
\end{figure}

@@

## Expected new infections reached

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=1]{depends/infections-reached-country.pdf}}
\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Botswana.}
\label{fig:infections-reached-country-1}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=2]{depends/infections-reached-country.pdf}}
\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Cameroon.}
\label{fig:infections-reached-country-2}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=3]{depends/infections-reached-country.pdf}}
\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Kenya.}
\label{fig:infections-reached-country-3}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=4]{depends/infections-reached-country.pdf}}
\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Lesotho.}
\label{fig:infections-reached-country-4}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=5]{depends/infections-reached-country.pdf}}
\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Mozambique.}
\label{fig:infections-reached-country-5}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=6]{depends/infections-reached-country.pdf}}
\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Malawi.}
\label{fig:infections-reached-country-6}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=7]{depends/infections-reached-country.pdf}}
\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Namibia.}
\label{fig:infections-reached-country-7}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=8]{depends/infections-reached-country.pdf}}
\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Eswatini.}
\label{fig:infections-reached-country-8}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=9]{depends/infections-reached-country.pdf}}
\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Tanzania.}
\label{fig:infections-reached-country-9}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=10]{depends/infections-reached-country.pdf}}
\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Uganda.}
\label{fig:infections-reached-country-10}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=11]{depends/infections-reached-country.pdf}}
\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in South Africa.}
\label{fig:infections-reached-country-11}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=12]{depends/infections-reached-country.pdf}}
\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zambia.}
\label{fig:infections-reached-country-12}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=13]{depends/infections-reached-country.pdf}}
\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zimbabwe.}
\label{fig:infections-reached-country-13}
\end{figure}
